Staged Abstract Interpreters

### 2019-03-23 paper/20_prelim.tex
reference

\subsection{Generic Interface} \label{generic_if}

Monad transformers are type constructors of kind @(* -> *) -> (* -> *)@, which
takes a monad as argument and produces another monad. By using monad transformers, 
we can combine multiple monads into a single one.
Constructing extensible interpreters using monad transformers was first proposed by \citet{DBLP:conf/popl/LiangHJ95},
and later has been applied to abstract interpreters \cite{Sergey:2013:MAI:2491956.2491979, DBLP:journals/pacmpl/DaraisLNH17}.
In section, with the multi-stage programming and monad transformers in mind
while leave them as abstract type members, we present the generic interface of
a big-step definitional interpreter.

>>>>

\subsection{Generic Interpreter} \label{generic_if}

Monad transformers are type constructors of kind @(* -> *) -> (* -> *)@, which
takes a monad as argument and produces another monad. By using monad transformers, 
we can combine multiple monads into a single one.
Constructing extensible interpreters using monad transformers was first proposed by \citet{DBLP:conf/popl/LiangHJ95},
and later has been applied to abstract interpreters \cite{Sergey:2013:MAI:2491956.2491979, DBLP:journals/pacmpl/DaraisLNH17, Darais:2015:GTM:2814270.2814308}.
In section, with the multi-stage programming and monad transformers in mind
while leave them as abstract type members, we present the generic interface of
a big-step definitional interpreter.
